Proposal full title \\ Proposal Acronym

### 2001-10-08 drafts/IST/PartA.tex
new objectives, and description of the work
svn path=/trunk/; revision=1483

been raised by the hosting facilities which provide most of the mandatory tools
that free software developers need for everyday tasks. But although there are

@@

them. NAME will of course provide the same services as current facilities but

@@

628 characters...

@@

\subsubsection{Context}
Most of free or open source software is collaboratively developped using an
hosting plateform. They are mostly web sites. The frontend integrates different
functionnalities that are available to project developpers and administrators
and linked them with each other. The backend is mainly implemented with
scripts. \\
Current hosting plaforms are implemented as a  web site that provides
functionnalities to developpers. The most common ones include  users and groups
of users management, project repository (usualy based on Concurent Versionning
System), per project web pages and document sharing, per project mailing lists
and web forums, bugtracking system, project management system (audit, task
management), global site management and information feeding. There is currently
four main web hosting facilities : SourceForge (http://sourceforge.net/),
Savannah (http://savannah.gnu.org/), VHFFS (http://tuxfamily.org/), nd
Picolibre (http://picolibre.eu.org/). In terms of number of users and projects,
Savannah and SourceForge are the leaders.
\subsubsection{Mission}
Although hosting facilities are widely used in the freesoftware community the
existing solutions have some drawbacks, that refrain their wide adoption as
well in the Libre software community than in the software industry. \\
Due to a quick design, they are hard to distribute. They mainly are a front end
to a group of dedicated machines that provides a precise set of
functionnalities. Even if the acces is remote, all data is centralized as one
site physically hosts an huge number of projects. This is bad practice in terms
of data safety, data access and scalability. \\
Also due to the number of services and their inter-relations, it is not simple
to set up a new site that provides hosting. This is a real brake to a large
number of sites using this technology.  There is no complete solutions to
install easily any of the technologies described above. \\
They rely too much on managing procedures and human control. For example, a
site needs to be managed by people that acknowledge project creation. \\
At last the most active effort to build such a sytem has recently become
proprietary.  Therefore the produced work is not available. 

@@

@@

>>>>

been raised by hosting facilities which provide most of the mandatory tools
that free software developers need for everyday tasks such as Bug tracking,
mailing lists, Project management... But although there are

@@

them.
NAME will of course provide the same services as current facilities but

@@

680 characters...

@@

The NAME project aims at developping a complete hosting facility. It composed
of two subprojects. \\
The first one is the NAME project that will be a next generation hosting
facility. It will provide a web frontend to a number of tools are now mandatory
for software development (user/groups rights management, bug tracking, mailing
lists and forums...). The main idea between its design is to make it
transparently distributed. At each step of its development, we will focus on
the ease of installation and configuration.
The second one is the "CoopX" project that will provide a generic description of
an hosting facility. With that tool we want to allow different kind of facility
to communicate each other. It will help to develop tools to facilitate
migrations between hosting facilities.
\\ 800 chars need some check and some other stuff:w

@@

%SAVANNAH
The hosting facility is composed of two main parts, the frontend and the
backend. The first one is the code base that interacts with the user and that
will implement services that are not provided by external software. The backend
will link the Database (filled by the frontend) to external software which
provide services such as DNS, mailing lists or CVS. Concurrently the packaging
of the solution will allow the validation and testing of each milestone.
% 450
%COOPX

@@

%%% HELP HELP
